### 2011-01-16 docs/tex/application.tex
Some additions in application and model design.

So the kind of problems we should be looking for applying the evolution of mimicry, are the ones which cannot be solved with conventional evolutionary methods. We should be looking for a problem where the idea of deception can be useful in term of solving it. Unfortunately during the time of this research we were unable to find such a problem.

>>>>

So the kind of problems we should be looking for applying the evolution of mimicry, are the ones which cannot be solved with conventional evolutionary methods. We should be looking for a problem where the idea of deception can be useful in term of solving it. An interesting analogy is with anti-virus and virus software. If we consider anti-virus to be predator and virus (mimic) to be prey species, then the objective of a virus would be to look like a regular virus free program (model) to get pass an anti-virus software. In this way if a virus can mimic a regular program then it will be able to get pass any anti-virus software available in the market. To successfully implement this software we need to create a virus program which can evolve itself to pretend like a regular program (virus free). The environment will be the operating system itself where all the programs reside. It is worth noting the fact that this objective is malicious for the computer industry, which makes it less significant to pursue.

### 2011-01-16 docs/tex/model.tex
Some additions in application and model design.

\subsection{Species diversity}
Franks and Noble have used different models to diversify species. In \cite{franks2002} they have used linear difference in number ``constrained to a 'ring' of values  from 1-20 (where 20 and 1 are neighbors)" to distinguish species diversity. Here the distance of one phenotype from another represents their level of similarity.

@@

\section{Conclusion}
This model has been designed from a practical point of view; to come up with efficient results and achieve the main objective, \textit{evolution of mimicry}. Creation and transformation of different mimicry ring and also the dynamics of it has been integrated to achieve interesting results. This model can also be considered as a complex adaptive system similar to Holland's work on Echo \cite{holland1996}. The seven basics of a complex adaptive system which are: Aggregation, Tagging, Nonlinearity, Flow, Diversity, Internal Models and Building blocks \cite{holland1996} are present in this model.

>>>>

\subsection{Species diversity}
\label{subsec:species-diversity}
Franks and Noble have used different models to diversify species. In \cite{franks2002} they have used linear difference in number ``constrained to a 'ring' of values  from 1-20 (where 20 and 1 are neighbors)" to distinguish species diversity. Here the distance of one phenotype from another represents their level of similarity.

@@

\section{Conclusion}
This model has been designed from a practical point of view; to come up with efficient results and achieve the main objective, \textit{evolution of mimicry}. Creation and transformation of different mimicry ring and also the dynamics of it has been integrated to achieve interesting results. This model can also be considered as a complex adaptive system similar to Holland's work on Echo \cite{holland1996}. The seven basics of a complex adaptive system which are: Aggregation, Tagging, Nonlinearity, Flow, Diversity, Internal Models and Building blocks \cite{holland1996} are present in this model. Individual components of this model such as the different types of agents and their properties can be considered as \textit{building blocks}. Each prey species are \textit{tagged} with individual pattern and palatability with which predators recognize them. We are providing different properties, behaviors and goals to the agents but setting them free in the environment to observe their \textit{aggregate} behavior, resulting in \textit{non-linear} or unpredictable outcome. The model has its \textit{flow} as it progresses in time. Also there is \textit{diversity} of prey species in the environment (\ref{subsec:species-diversity}).

To explain internal model for a complex adaptive system Holland has used specifically the example of evolution of mimicry \cite{holland1996}. He choose to use the term `Internal Model' to refer to the mechanism for anticipation. Predators in this model anticipate the bitter taste of prey, by making intelligent decisions for consuming them. This mechanism for anticipation can be considered as the property of \textit{internal model} for this specific study.
